Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-12-05 ms/ms.Rmd
ms: add groups to preds table

We created the same suite of peat depth predictors for both sites (25 continuous and 1 categorical; Table \@ref(tab:preds)).
All continuous predictors were derived either from an airborne radiometric survey or from a DTM.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the DTMs we calculated several land surface parameters, ranging from simple terrain indices to more complex geomorphometric and hydrological variables [@maxwellLandsurfaceParametersSpatial2022].
The categorical predictor was peat depth class, from a national map dataset.
Complete descriptions of predictors follow below.
```{r preds, echo=FALSE, message=FALSE}
df <- readr::read_csv("tables/predictors.csv")
knitr::kable(df, booktabs = FALSE, vline = "", linesep = "",
             col.names = c("Name", "Description"),
             caption = "Candidate predictors of peat depth.")
```

>>>>

We created the same suite of peat depth predictors for both sites (25 continuous and 1 categorical; Table \@ref(tab:preds)).
All continuous predictors were derived either from an airborne radiometric survey or from a DTM.
From the radiometric surveys we simply used the four variables produced by the surveyors (Geological Survey of Norway): ground concentration of Potassium, Thorium, Uranium, as well as total count.
From the DTMs we calculated several land surface parameters, ranging from simple terrain indices to more complex geomorphometric and hydrological variables [@maxwellLandsurfaceParametersSpatial2022].
The categorical predictor was peat depth class, from a national map dataset.
Complete descriptions of predictors follow below.
```{r preds, echo=FALSE, message=FALSE}
df <- readr::read_csv("tables/predictors.csv")
options(knitr.kable.NA = '')
knitr::kable(df, booktabs = FALSE, vline = "", linesep = "",
             col.names = c("Group", "Name", "Description"),
             caption = "Candidate predictors of peat depth.")
```

### 2024-12-05 ms/ms.tex
ms: add groups to preds table

\caption{\label{tab:preds}Candidate predictors of peat depth.}
\centering
\begin{tabular}[t]{ll}
\hline
Name & Description\\
\hline
radK & Potassium ground concentration\\
radTh & Thorium ground concentration\\
radU & Uranium ground concentration\\
radTC & Total count of gamma radiation\\
elevation & Mean elevation\\
slope1m & Mean of 1 m slope\\
TPI1m & Mean of 1 m topographic position index\\
TRI1m & Mean of 1 m terrain ruggedness index\\
roughness1m & Mean of 1 m roughness\\
slope10m & 10 m slope\\
TPI10m & 10 m topographic position index\\
TRI10m & 10 m terrain ruggedness index\\
roughness10m & 10 m roughness\\
MRVBF & Multi-resolution valley bottom flatness\\
TWI5m & Mean of 5 m topographic wetness index\\
TWI10m & 10 m topographic wetness index\\
TWI20m & Bilinear interpolation of 20 m topographic wetness index\\
TWI50m & Bilinear interpolation of 50 m topographic wetness index\\
DTW2500 & Depth-to-water index, flow initiation area of 0.25 ha\\
DTW5000 & Depth-to-water index, flow initiation area of 0.5 ha\\
DTW10000 & Depth-to-water index, flow initiation area of 1 ha\\
DTW20000 & Depth-to-water index, flow initiation area of 2 ha\\
DTW40000 & Depth-to-water index, flow initiation area of 4 ha\\
DTW80000 & Depth-to-water index, flow initiation area of 8 ha\\
DTW160000 & Depth-to-water index, flow initiation area of 16 ha\\
DMK & DMK peat depth class, categorical with 3 levels\\
\hline
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:preds}Candidate predictors of peat depth.}
\centering
\begin{tabular}[t]{lll}
\hline
Group & Name & Description\\
\hline
radiometric & radK & Potassium ground concentration\\
 & radTh & Thorium ground concentration\\
 & radU & Uranium ground concentration\\
 & radTC & Total count of gamma radiation\\
terrain & elevation & Mean elevation\\
 & slope1m & Mean of 1 m slope\\
 & TPI1m & Mean of 1 m topographic position index\\
 & TRI1m & Mean of 1 m terrain ruggedness index\\
 & roughness1m & Mean of 1 m roughness\\
 & slope10m & 10 m slope\\
 & TPI10m & 10 m topographic position index\\
 & TRI10m & 10 m terrain ruggedness index\\
 & roughness10m & 10 m roughness\\
 & MRVBF & Multi-resolution valley bottom flatness\\
 & TWI5m & Mean of 5 m topographic wetness index\\
 & TWI10m & 10 m topographic wetness index\\
 & TWI20m & Bilinear interpolation of 20 m topographic wetness index\\
 & TWI50m & Bilinear interpolation of 50 m topographic wetness index\\
 & DTW2500 & Depth-to-water index, flow initiation area of 0.25 ha\\
 & DTW5000 & Depth-to-water index, flow initiation area of 0.5 ha\\
 & DTW10000 & Depth-to-water index, flow initiation area of 1 ha\\
 & DTW20000 & Depth-to-water index, flow initiation area of 2 ha\\
 & DTW40000 & Depth-to-water index, flow initiation area of 4 ha\\
 & DTW80000 & Depth-to-water index, flow initiation area of 8 ha\\
 & DTW160000 & Depth-to-water index, flow initiation area of 16 ha\\
existing map & DMK & DMK peat depth class, categorical with 3 levels\\
\hline
\end{tabular}
\end{table}
